6.867 Problem Set 1

### 2015-12-09 Project/Latex/Paper.tex
[project] mse plots.
[project] some tidying up.
[project] some new plots.

@@

%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering

>>>>

\begin{figure}[ht]\centering
\includegraphics[width=\linewidth]{author_popularity_histogram.png}
\caption{Histogram of Bing Search Results}
\label{fig:ap_hist}
\end{figure}

\begin{figure}[ht]\centering
\includegraphics[width=\linewidth]{author_popularity_log_histogram.png}
\caption{Histogram of log(Bing Search Results)}
\label{fig:apl_hist}
\end{figure}

\begin{figure}[ht]\centering
\includegraphics[width=\linewidth]{flesch_data_histogram.png}
\caption{Histogram of Flesch Reading Ease}
\label{fig:fre_hist}
\end{figure}

@@

\begin{figure*}[ht]\centering
\includegraphics[width=\linewidth]{feature_weights.png}
\caption{Linear Regression Feature Weights (excluding intercept term)}
\label{fig:lin_reg_weights}
\end{figure*}

\begin{figure}[ht]\centering
\includegraphics[width=\linewidth]{mse_plot.png}
\caption{The effect of regularization on MSE}
\label{fig:mse_plot}
\end{figure}

\begin{center}
\begin{tabular}{lr}
\toprule
Feature  &  Weight\\
\midrule
intercept & 9.114\\
log(Word Count) & 0.736\\
Desk: Foreign & 0.561\\
Desk: Travel & -0.478\\
Section: World & -0.410\\
Type: BlogPost & -0.394\\
Type of Material: Schedule & -0.330\\
Type of Material: Review & -0.324\\
Type of Material: Letter & -0.311\\
Section: Fashion \& Style & 0.275\\
Section: Movies & -0.267\\
Desk: National & 0.245\\
Section: Opinion & 0.245\\
Time of Day: 12-17 & 0.239\\
Section: Books & 0.219\\
Section: Health & 0.200\\
Section: Sports & -0.191\\
Desk: Society & -0.178\\
Section: Corrections & -0.167\\
Desk: BookReview & -0.167\\
\end{tabular}
\end{center}
%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering
